---
title: "p8105_hw5_lg3158"
author: "Ling"
date: "11/12/2021"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(rvest)
library(httr)
library(stringr)
```

## Problem 1
```{r}
q1_df = 
  read_csv(url("https://github.com/washingtonpost/data-homicides/raw/master/homicide-data.csv")) %>%
  mutate(city_state = paste(city, state, sep = ","))
```

- The data have `r nrow(q1_df)` observations and `r ncol(q1_df)` variables (`r ls(q1_df)`) after create the `city_state` variable.
- Summarize total homicide and unsolved homicide
  - create a data summarize total homicide number by city
  - create a data only including the unsolved homicide, and summarize the total number by city
  - combine the 2 data by city
  - show the first 5 rows
```{r}
q1_tot = q1_df %>%
  group_by(city_state) %>%
  summarise(total = n())

q1_unsolved = q1_df %>%
  filter(disposition %in% c("Closed without arrest","Open/no arrest")) %>%
  group_by(city_state) %>%
  summarise(unsolved = n())

q1_summary = left_join(q1_tot, q1_unsolved, by = "city_state")

knitr::kable(q1_summary[1:5, ])
```

- `prop.test`
  - Baltimore result
```{r}
q1_balt =
  prop.test(pull(subset(q1_summary, city_state == "Baltimore,MD"),unsolved), 
            pull(subset(q1_summary, city_state == "Baltimore,MD"),total)) %>%
  broom::tidy() %>%
  mutate(city_state = "Baltimore,MD") %>%
  select(city_state, estimate, conf.low, conf.high)
knitr::kable(q1_balt)
```

  - all other cities result, show the first 5 rows
```{r}
fx_proc = function(dat)
  {
  if (is.na(dat$unsolved))
  {
    return(c(NA, NA, NA))
  }
  
  prop = prop.test(dat$unsolved, dat$total) %>%
    broom::tidy() %>%
    select(estimate, conf.low, conf.high)
  return(prop)
}

q1_list = 
  nest(q1_summary, data = total:unsolved)

q1_list_result = q1_list %>%
mutate(result = map(q1_list$data, fx_proc)) %>%
  unnest(cols = c(data, result)) %>%
  select(-result)

knitr::kable(q1_list_result[1:5, ])
```

  - plot for unsolved homicide cases
```{r}
q1_plot = q1_list_result %>%
  ggplot(aes(x = city_state, y = estimate*100)) +
    geom_bar(stat = "identity") +
    geom_errorbar(aes(ymin = conf.low*100, ymax = conf.high*100), stat = "identity") +
    labs(title = "Unsolved homicide proportions",
         x = "City, state",
         y = "Unsolved case(%)") +
  coord_flip()

q1_plot
```

## Problem 2

- download and unzip the zip file
- construct a dataframe which contains
  - all the file name (`filename`)
  - from `filename`, extract experimental arm or control arm (`arm`) and subject id (`ID`)
  - read in data (a list named as `data`)
    - before read in data, create a function named `readin` to load the csv data
  - unnest the list `data`
  - make `arm` values more readable
  - drop `filename`
  - make the columns `week_01`-`week_08` into 2 columns: `fu_time` and `value`
- show the first 10 rows
```{r}
download.file(url = "https://www.p8105.com/data/hw5_data.zip", destfile = "./data/hw5_data.zip")
unzip("./data/hw5_data.zip", exdir = ".")


readin = function(indata){
  data = read_csv(file = paste("./data/",indata, sep = ""))
  return(data)
}

q2_files = tibble(
  filename = list.files(path = "./data", pattern = "*.csv"),
  arm = substring(filename, 1,3),
  ID = substring(filename, 1,6),
  data = map(filename,readin)
  ) %>%
  unnest(cols = data) %>%
  mutate(arm = if_else(arm == "con", "control arm", "experimental arm")) %>%
  select(-filename) %>%
  pivot_longer(cols = starts_with("week_"), names_to = "fu_time", names_prefix = "week_", values_to = "value") %>%
  mutate(fu_time = as.numeric(fu_time))

knitr::kable(q2_files[1:10, ])
```

- the spaghetti plot
```{r}
q2_plot = q2_files %>%
  ggplot(aes(x = fu_time, y = value, color = arm, group = ID)) +
    geom_line(alpha = 0.5, size = 2) +
    geom_smooth(aes(group = arm), se = F, size = 4) +
    labs(x = "follow-up time (week)") +
    theme_minimal()
q2_plot
```

  - from the plot, we can see that the baseline values between the 2 arms are similar, with different trends during the follow-up. The control arm almost kept constant while the experimental arm increased.
  
## Problem 3

- create a function taking 1 vector (list) as an argument
  - missing value imputation
- using map to do the missing value imputation
  - print the first 10 rows of the original data
  - transform the original data into list, using `nest`
  - using `map`
- transform the result list into a dataframe
  - print the first 10 rows

```{r}
set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))

knitr::kable(iris_with_missing[1:10, ])

iris_list = iris_with_missing %>%
  nest(data = everything())
 
 fillin = function(var) {
  if (is.numeric(var)) {
    for (i in 1:150) {
    var[[i]] = if_else(is.na(var[[i]]), mean(var, na.rm = T), var[[i]])
    }
  }
  
  if (is.character(var)) {
    for (i in 1:150) {
      var[[i]] = if_else(is.na(var[[i]]),"virginica", var[[i]])
    }
  }
  return(var)
 }
 
iris_fill = tibble(
  var = c("Sepal.Length", "Sepal.Width", "Petal.Length","Petal.Width","Species"),
  fill = map(iris_list$data[[1]], fillin)) %>%
  pivot_wider(names_from = var, values_from = fill) %>%
  unnest( cols = c("Sepal.Length", "Sepal.Width", "Petal.Length","Petal.Width","Species"))

knitr::kable(iris_fill[1:10, ])
```


