---
title: "p8105_hw5_lg3158"
author: "Ling"
date: "11/12/2021"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(rvest)
library(httr)
library(stringr)
```

## Problem 1
```{r}
q1_df = 
  read_csv(url("https://github.com/washingtonpost/data-homicides/raw/master/homicide-data.csv")) %>%
  mutate(city_state = paste(city, state, sep = ","))
```

- The data have `r nrow(q1_df)` observations and `r ncol(q1_df)` variables (`r ls(q1_df)`) after create the `city_state` variable.
- Summarize total homicide and unsolved homicide
  - create a data summarize total homicide number by city
  - create a data only including the unsolved homicide, and summarize the total number by city
  - combine the 2 data by city
  
```{r}
q1_tot = q1_df %>%
  group_by(city_state) %>%
  summarise(total = n())

q1_unsolved = q1_df %>%
  filter(disposition %in% c("Closed without arrest","Open/no arrest")) %>%
  group_by(city_state) %>%
  summarise(unsolved = n())

q1_summary = left_join(q1_tot, q1_unsolved, by = "city_state")

knitr::kable(q1_summary)
```

- `prop.test`
  - Baltimore result
```{r}
q1_balt =
  prop.test(pull(subset(q1_summary, city_state == "Baltimore,MD"),unsolved), 
            pull(subset(q1_summary, city_state == "Baltimore,MD"),total)) %>%
  broom::tidy() %>%
  mutate(city_state = "Baltimore,MD") %>%
  select(city_state, estimate, conf.low, conf.high)
knitr::kable(q1_balt)
```

  - all other cities result
```{r}
fx_proc = function(dat)
  {
  if (is.na(dat$unsolved))
  {
    return(c(NA, NA, NA))
  }
  
  prop = prop.test(dat$unsolved, dat$total) %>%
    broom::tidy() %>%
    select(estimate, conf.low, conf.high)
  return(prop)
}

q1_list = 
  nest(q1_summary, data = total:unsolved)

q1_list_result = q1_list %>%
mutate(result = map(q1_list$data, fx_proc)) %>%
  unnest(cols = c(data, result)) %>%
  select(-result)

knitr::kable(q1_list_result)
```

  - plot for unsolved homicide cases
```{r}
q1_plot = q1_list_result %>%
  ggplot(aes(x = city_state, y = estimate*100)) +
    geom_bar(stat = "identity") +
    geom_errorbar(aes(ymin = conf.low*100, ymax = conf.high*100), stat = "identity") +
    labs(title = "Unsolved homicide proportions",
         x = "City, state",
         y = "Unsolved case(%)") +
  coord_flip()

q1_plot
```

## Problem 2



